Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-08-25 Response to reviewers.tex

%------------------------------------------------------------------------------------
\section{Comments by Reviewer \#1}

\noindent \emph{There are some issues needed to be addressed further:} \\

\noindent (1) \emph{Generally speaking, predicting sales is regarded as a regression probelm (numerical output) rather than classification (categorical one). Both CFS and RelieFF are originally designed for classification problem. When CFS is used for regression, please to introduce how to estimate correlations between each feature and output (total sales). Since RReliefF, as a variant of ReliefF, is special for regression, why do not the authors use RReliefF? }

\begin{verbatim}
In all our experiments we have applied the Weka's implementation of the ReliefF algorithm in the regression problems. This version is called "Regressional ReliefF" or "RReliefF" for short which was first introduced and implemented by Robnik-Sikonja and Kononenko in Ref XX for numeric targets. Therefore, we have clarified this point in the text to remove any ambiguity.

For CSF, estimating the correlation between attributes is standard linear (Pearson's) correlation.
The details have been added to the text to clarify this point.
\end{verbatim}

### 2016-08-29 paper.tex
Added a brief description of ELM

>>>>

\item \emph{Extreme learning machine (ELM)}: 
ELM is an algorithm for training a single hidden 
layer feedforward neural network which was first proposed by Guang-Bin Huang \cite
{huang2006extreme}. A typical implementation of ELM is a single hidden layer network where the 
connection weights between the input layer and the hidden layer are randomly initialized and 
fixed, while the connection weights between the hidden layer the output layer are learned 
analytically in a single step of linear parameters solving. In ELM the hidden layer maps the 
input data into a feature space called ELM feature space using non-linear activation functions 
such as Sigmoid, Hyperbolic and Gaussian functions \cite{huang2015trends}.The main advantages 
of ELM are the ease of use and the very efficient learning speed compared to other traditional 
training methods such as the Backpropagation algorithm.
